---
title: "Detailed Results"
subtitle: "Can reflective diary-writing increase sufficiency-oriented consumption? A longitudinal intervention addressing the role of basic psychological needs, well-being, and time-affluence"
author: "Marlis Wullenkord and Josephine Tröger"
date: '2020-12-29'
output:
  html_document:
    fig_height: 9
    fig_width: 16
    highlight: default
    number_sections: yes
    theme: yeti
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}
# Data cleaning
## Loading packages I

library(psych)
library(dplyr)
library(car)
library(janitor)
```

```{r}
## T1
### Loading data

d1 <- read.csv("Analysis_Troeger_et_al_2022/Datasets/Pre.csv", header = TRUE, sep = ",")
```

```{r}
### Preparing the data

length(unique(d1$case)) == nrow(d1)
which(duplicated(d1$case)) 
d2 <- d1[!duplicated(d1$case),] 
d2.1 <- d1[duplicated(d1$case),] 
which(d2$case == 103)
d3 <- d2 [-c(103), ] 
d4 <- subset(d3, case != "NA") 
data <- d4
```

```{r}
### Define Missings 

is.na(data$age.t1) <- which(data$age.t1== 0)
```

```{r}
### Calculating means T1
#### Subjective well-being 
# Inverting items

data$swb7.t1.i <- recode (data$swb7.t1, '1=5; 2=4; 4=2; 5=1')
data$swb8.t1.i <- recode (data$swb8.t1, '1=5; 2=4; 4=2; 5=1')
data$swb9.t1.i <- recode (data$swb9.t1, '1=5; 2=4; 4=2; 5=1')
data$swb10.t1.i <- recode (data$swb10.t1, '1=5; 2=4; 4=2; 5=1')
data$swb11.t1.i <- recode (data$swb11.t1, '1=5; 2=4; 4=2; 5=1')
data$swb12.t1.i <- recode (data$swb12.t1, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#Calculating mean subjective well-being 

data$swb.t1 <- rowMeans (data [c("swb1.t1", "swb2.t1", "swb3.t1", "swb4.t1", 
                                 "swb5.t1", "swb6.t1", "swb7.t1.i", "swb8.t1.i",
                                 "swb9.t1.i", "swb10.t1.i", "swb11.t1.i", "swb12.t1.i")]) 
```

```{r}
#### Time affluence 
#Inverting items

data$t1.t1.i <- recode (data$t1.t1, '1=5; 2=4; 4=2; 5=1')
data$t3.t1.i <- recode (data$t3.t1, '1=5; 2=4; 4=2; 5=1')
data$t6.t1.i <- recode (data$t6.t1, '1=5; 2=4; 4=2; 5=1')
data$t8.t1.i <- recode (data$t8.t1, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#Calculating mean time affluence

data$t.t1 <- rowMeans (data [c("t1.t1.i", "t2.t1", "t3.t1.i", "t4.t1",
                               "t5.t1", "t6.t1.i", "t7.t1", "t8.t1.i")])
```

```{r}
#### Basic psychological needs
#Inverting items

data$gbk16.t1.i <- recode (data$gbk16.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk17.t1.i <- recode (data$gbk17.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk18.t1.i <- recode (data$gbk18.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')

data$gbk3.t1.i <- recode (data$gbk3.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk4.t1.i <- recode (data$gbk4.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk5.t1.i <- recode (data$gbk5.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')

data$gbk8.t1.i <- recode (data$gbk8.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk10.t1.i <- recode (data$gbk10.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk11.t1.i <- recode (data$gbk11.t1, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
```

```{r}
#Calculating means basic psychological needs

data$gbk.t1.r <- rowMeans (data [c("gbk13.t1", "gbk14.t1", "gbk15.t1",
                                   "gbk16.t1.i", "gbk17.t1.i", "gbk18.t1.i")]) #relatedness satisfaction

data$gbk.t1.a <- rowMeans (data [c("gbk1.t1", "gbk2.t1", "gbk6.t1",
                                   "gbk3.t1.i", "gbk4.t1.i", "gbk5.t1.i")])    #autonomy satisfaction

data$gbk.t1.c <- rowMeans (data [c("gbk9.t1", "gbk12.t1",
                                   "gbk8.t1.i", "gbk10.t1.i", "gbk11.t1.i")])  #competence satisfaction


data$gbk.t1.s <- rowMeans (data [c("gbk13.t1", "gbk14.t1", "gbk15.t1",
                               "gbk16.t1.i", "gbk17.t1.i", "gbk18.t1.i",
                               "gbk1.t1", "gbk2.t1", "gbk6.t1",
                               "gbk3.t1.i", "gbk4.t1.i", "gbk5.t1.i",
                               "gbk9.t1", "gbk12.t1",
                               "gbk8.t1.i", "gbk10.t1.i", "gbk11.t1.i")])      #basic needs satisfaction
```


```{r}
#### Sufficiency orientation
#Inverting items

data$so4.t1.i <- recode (data$so4.t1, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#z-standardizing items

data$sv1.t1.z <- scale(data$sv1.t1)
data$sv2.t1.z <- scale(data$sv2.t1)
data$sv3.t1.z <- scale(data$sv3.t1)
data$sv4.t1.z <- scale(data$sv4.t1)
data$sv5.t1.z <- scale(data$sv5.t1)
data$sv6.t1.z <- scale(data$sv6.t1)
data$sv12.t1.z <- scale(data$sv12.t1)
data$sv13.t1.z <- scale(data$sv13.t1)
data$sv14.t1.z <- scale(data$sv14.t1)
data$sv15.t1.z <- scale(data$sv15.t1)
data$sv16.t1.z <- scale(data$sv16.t1)
data$sv17.t1.z <- scale(data$sv17.t1)
data$sv18.t1.z <- scale(data$sv18.t1)

data$so1.t1.z <- scale(data$so1.t1)
data$so2.t1.z <- scale(data$so2.t1)
data$so3.t1.z <- scale(data$so3.t1)
data$so4.t1.i.z <- scale(data$so4.t1.i)
data$so5.t1.z <- scale(data$so5.t1)
data$so6.t1.z <- scale(data$so6.t1)
data$so7.t1.z <- scale(data$so7.t1)
data$so8.t1.z <- scale(data$so8.t1)
data$so9.t1.z <- scale(data$so9.t1)
data$so10.t1.z <- scale(data$so10.t1)
data$so11.t1.z <- scale(data$so11.t1)
data$so12.t1.z <- scale(data$so12.t1)
data$so13.t1.z <- scale(data$so13.t1)
```

```{r}
#Calculating mean sufficiency orientation

data$s.t1 <- rowMeans (data [c("so1.t1.z", "so2.t1.z", "so4.t1.i.z", "so5.t1.z",
                               "so6.t1.z", "so8.t1.z", "so9.t1.z", "so10.t1.z",
                               "so11.t1.z", "so12.t1.z", "so13.t1.z",
                               "sv1.t1.z", "sv2.t1.z", "sv3.t1.z", "sv4.t1.z",
                               "sv5.t1.z", "sv6.t1.z",
                               "sv12.t1.z", "sv13.t1.z", "sv14.t1.z", "sv15.t1.z",
                               "so7.t1.z",
                               "sv16.t1.z", "sv17.t1.z", "sv18.t1.z", "so3.t1.z")])
```

```{r}
#### Self-reflection

data$sr.t1 <- rowMeans (data [c("sr1.t1", "sr2.t1", "sr3.t1", "sr4.t1",
                                "sr5.t1", "sr7.t1")]) 
```

```{r}
#### Standardized scales T1

# Sufficiency orientation
data$s.t1.z <- scale(data [,"s.t1"])

# Subjective wellbeing
data$swb.t1.z <- scale(data [,"swb.t1"])

# Basic psychological needs
data$gbk.t1.s.z <- scale(data [,"gbk.t1.s"])

# Time affluence
data$t.t1.z <- scale(data [,"t.t1"])

# Self-reflection
data$sr.t1.z <- scale(data [,"sr.t1"])
```

```{r}
### Calculating outliers T1

d.t1 <- filter (data, ok.t1 == 1 & dauer.t1 > 0 & (check.t1 == 4 | is.na(check.t1))) 

d.t1.a <- filter(d.t1, s.t1.z <= 2.5 & s.t1.z >= (-2.5)
                & swb.t1.z <= 2.5 & swb.t1.z >= (-2.5)
                & gbk.t1.s.z  <= 2.5 & gbk.t1.s.z >= (-2.5) 
                & t.t1.z  <= 2.5 & t.t1.z >= (-2.5)
                & sr.t1.z <= 2.5 & sr.t1.z >= (-2.5))
```

```{r}
### Renaming dataset T1

table_pre <- d.t1.a
```

```{r}
## T2
### Loading data

table1 <- read.csv("Analysis_Troeger_et_al_2022/Datasets/EG_Post.csv", header = TRUE, sep = ",")
table2 <- read.csv("Analysis_Troeger_et_al_2022/Datasets/CG_Post.csv", header = TRUE, sep = ",")
table3 <- read.csv("Analysis_Troeger_et_al_2022/Datasets/Check.csv", header = TRUE, sep = ";")
```

```{r}
### Merging data

d1 <- merge(table1, table2, all=TRUE) 
d2 <- full_join(d1, table3, by = c ("case", "bed")) 
```

```{r}
### Preparing the data

length(unique(d2$case)) == nrow(d2)
which(duplicated(d2$case)) 
d3 <- d2[!duplicated(d2$case),] 
d3.1 <- d2[duplicated(d2$case),]
d4 <- subset(d3, case != "NA") 
data <- d4
```

```{r}
### Define Missings 

is.na(data$age.t2) <- which(data$age.t2== 0) 
```

```{r}
### Calculating means T2
#### Subjective well-being
#Inverting items

data$swb7.t2.i <- recode (data$swb7.t2, '1=5; 2=4; 4=2; 5=1')
data$swb8.t2.i <- recode (data$swb8.t2, '1=5; 2=4; 4=2; 5=1')
data$swb9.t2.i <- recode (data$swb9.t2, '1=5; 2=4; 4=2; 5=1')
data$swb10.t2.i <- recode (data$swb10.t2, '1=5; 2=4; 4=2; 5=1')
data$swb11.t2.i <- recode (data$swb11.t2, '1=5; 2=4; 4=2; 5=1')
data$swb12.t2.i <- recode (data$swb12.t2, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#Calculating mean subjective well-being

data$swb.t2 <- rowMeans (data [c("swb1.t2", "swb2.t2", "swb3.t2", "swb4.t2", 
                                 "swb5.t2", "swb6.t2", "swb7.t2.i", "swb8.t2.i",
                                 "swb9.t2.i", "swb10.t2.i", "swb11.t2.i", "swb12.t2.i")]) 
```

```{r}
#### Time affluence
#Inverting items

data$t1.t2.i <- recode (data$t1.t2, '1=5; 2=4; 4=2; 5=1')
data$t3.t2.i <- recode (data$t3.t2, '1=5; 2=4; 4=2; 5=1')
data$t6.t2.i <- recode (data$t6.t2, '1=5; 2=4; 4=2; 5=1')
data$t8.t2.i <- recode (data$t8.t2, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#Calculating mean time affluence

data$t.t2 <- rowMeans (data [c("t1.t2.i", "t2.t2", "t3.t2.i", "t4.t2",
                               "t5.t2", "t6.t2.i", "t7.t2", "t8.t2.i")])
```

```{r}
#### Basic psychological needs
#Inverting items

data$gbk16.t2.i <- recode (data$gbk16.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk17.t2.i <- recode (data$gbk17.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk18.t2.i <- recode (data$gbk18.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')

data$gbk3.t2.i <- recode (data$gbk3.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk4.t2.i <- recode (data$gbk4.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk5.t2.i <- recode (data$gbk5.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')

data$gbk8.t2.i <- recode (data$gbk8.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk10.t2.i <- recode (data$gbk10.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk11.t2.i <- recode (data$gbk11.t2, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
```

```{r}
#Calculating means basic psychological needs

data$gbk.t2.r <- rowMeans (data [c("gbk13.t2", "gbk14.t2", "gbk15.t2",
                                   "gbk16.t2.i", "gbk17.t2.i", "gbk18.t2.i")])   #relatedness satisfaction

data$gbk.t2.a <- rowMeans (data [c("gbk1.t2", "gbk2.t2", "gbk6.t2",
                                   "gbk3.t2.i", "gbk4.t2.i", "gbk5.t2.i")])    #autonomy satisfaction

data$gbk.t2.c <- rowMeans (data [c("gbk9.t2", "gbk12.t2",
                                   "gbk8.t2.i", "gbk10.t2.i", "gbk11.t2.i")])  #competence satisfaction


data$gbk.t2.s <- rowMeans (data [c("gbk13.t2", "gbk14.t2", "gbk15.t2",
                                   "gbk16.t2.i", "gbk17.t2.i", "gbk18.t2.i",
                                   "gbk1.t2", "gbk2.t2", "gbk6.t2",
                                   "gbk3.t2.i", "gbk4.t2.i", "gbk5.t2.i",
                                   "gbk9.t2", "gbk12.t2",
                                   "gbk8.t2.i", "gbk10.t2.i", "gbk11.t2.i")])  #basic needs satisfaction
```

```{r}
#### Sufficiency orientation
#Inverting items

data$so4.t2.i <- recode (data$so4.t2, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#z-standardizing items

data$sv1.t2.z <- scale(data$sv1.t2)
data$sv2.t2.z <- scale(data$sv2.t2)
data$sv3.t2.z <- scale(data$sv3.t2)
data$sv4.t2.z <- scale(data$sv4.t2)
data$sv5.t2.z <- scale(data$sv5.t2)
data$sv6.t2.z <- scale(data$sv6.t2)
data$sv12.t2.z <- scale(data$sv12.t2)
data$sv13.t2.z <- scale(data$sv13.t2)
data$sv14.t2.z <- scale(data$sv14.t2)
data$sv15.t2.z <- scale(data$sv15.t2)
data$sv16.t2.z <- scale(data$sv16.t2)
data$sv17.t2.z <- scale(data$sv17.t2)
data$sv18.t2.z <- scale(data$sv18.t2)

data$so1.t2.z <- scale(data$so1.t2)
data$so2.t2.z <- scale(data$so2.t2)
data$so3.t2.z <- scale(data$so3.t2)
data$so4.t2.i.z <- scale(data$so4.t2.i)
data$so5.t2.z <- scale(data$so5.t2)
data$so6.t2.z <- scale(data$so6.t2)
data$so7.t2.z <- scale(data$so7.t2)
data$so8.t2.z <- scale(data$so8.t2)
data$so9.t2.z <- scale(data$so9.t2)
data$so10.t2.z <- scale(data$so10.t2)
data$so11.t2.z <- scale(data$so11.t2)
data$so12.t2.z <- scale(data$so12.t2)
data$so13.t2.z <- scale(data$so13.t2)
```

```{r}
#Calculating mean sufficiency orientation

data$s.t2 <- rowMeans (data [c("so1.t2.z", "so2.t2.z", "so4.t2.i.z", "so5.t2.z",
                               "so6.t2.z", "so8.t2.z", "so9.t2.z", "so10.t2.z",
                               "so11.t2.z", "so12.t2.z", "so13.t2.z",
                               "sv1.t2.z", "sv2.t2.z", "sv3.t2.z", "sv4.t2.z",
                               "sv5.t2.z", "sv6.t2.z",
                               "sv12.t2.z", "sv13.t2.z", "sv14.t2.z", "sv15.t2.z",
                               "so7.t2.z",
                               "sv16.t2.z", "sv17.t2.z", "sv18.t2.z", "so3.t2.z")])    
```

```{r}
#### Self-reflection

data$sr.t2 <- rowMeans (data [c("sr1.t2", "sr2.t2", "sr3.t2", "sr4.t2",
                                "sr5.t2", "sr7.t2")]) 
```

```{r}
#### Standardized scales T2

# Sufficiency orientation
data$s.t2.z <- scale(data [,"s.t2"])

# Subjective wellbeing
data$swb.t2.z <- scale(data [,"swb.t2"])

# Basiy psychological needs
data$gbk.t2.s.z <- scale(data [,"gbk.t2.s"])

# Time affluence
data$t.t2.z <- scale(data [,"t.t2"])

# Self-reflection
data$sr.t2.z <- scale(data [,"sr.t2"])
```

```{r}
### Calculating outliers

d.t2 <- filter(data, ok.t2 == 1 & dauer.t2 > 0 & sumcheck > 3 & (check.t2 == 4 | is.na(check.t2))) 

d.t2.a <- filter(d.t2, s.t2.z <= 2.5 & s.t2.z >= (-2.5)
                & swb.t2.z <= 2.5 & swb.t2.z >= (-2.5) 
                & gbk.t2.s.z  <= 2.5 & gbk.t2.s.z >= (-2.5) 
                & t.t2.z  <= 2.5 & t.t2.z >= (-2.5)
                & sr.t2.z  <= 2.5 & sr.t2.z >= (-2.5)) 
```

```{r}
### Renaming dataset T2

table_post <- d.t2.a
```


```{r}
## T3
### Loading data

d1 <- read.csv("Analysis_Troeger_et_al_2022/Datasets/FollowUp.csv", header = TRUE, sep = ",")
```

```{r}
### Preparing the data

length(unique(d1$case)) == nrow(d1)
which(duplicated(d1$case)) 
d2 <- d1[!duplicated(d1$case),] 
d2.1 <- d1[duplicated(d1$case),]
d3 <- subset(d2, case != "NA")
data <- d3
```

```{r}
### Define Missings 

is.na(data$age.t3) <- which(data$age.t3== 0)
```

```{r}
### Calculating means T3
#### Subjective well-being
#Inverting items

data$swb7.t3.i <- recode (data$swb7.t3, '1=5; 2=4; 4=2; 5=1')
data$swb8.t3.i <- recode (data$swb8.t3, '1=5; 2=4; 4=2; 5=1')
data$swb9.t3.i <- recode (data$swb9.t3, '1=5; 2=4; 4=2; 5=1')
data$swb10.t3.i <- recode (data$swb10.t3, '1=5; 2=4; 4=2; 5=1')
data$swb11.t3.i <- recode (data$swb11.t3, '1=5; 2=4; 4=2; 5=1')
data$swb12.t3.i <- recode (data$swb12.t3, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#Calculating mean subjective well-being

data$swb.t3 <- rowMeans (data [c("swb1.t3", "swb2.t3", "swb3.t3", "swb4.t3", 
                                 "swb5.t3", "swb6.t3", "swb7.t3.i", "swb8.t3.i",
                                 "swb9.t3.i", "swb10.t3.i", "swb11.t3.i", "swb12.t3.i")]) 
```

```{r}
#### Time affluence
#Inverting items

data$t1.t3.i <- recode (data$t1.t3, '1=5; 2=4; 4=2; 5=1')
data$t3.t3.i <- recode (data$t3.t3, '1=5; 2=4; 4=2; 5=1')
data$t6.t3.i <- recode (data$t6.t3, '1=5; 2=4; 4=2; 5=1')
data$t8.t3.i <- recode (data$t8.t3, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#Calculating mean time affluence

data$t.t3 <- rowMeans (data [c("t1.t3.i", "t2.t3", "t3.t3.i", "t4.t3",
                               "t5.t3", "t6.t3.i", "t7.t3", "t8.t3.i")])
```

```{r}
#### Basic psychological needs
#Inverting items

data$gbk16.t3.i <- recode (data$gbk16.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk17.t3.i <- recode (data$gbk17.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk18.t3.i <- recode (data$gbk18.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')

data$gbk3.t3.i <- recode (data$gbk3.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk4.t3.i <- recode (data$gbk4.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk5.t3.i <- recode (data$gbk5.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')

data$gbk8.t3.i <- recode (data$gbk8.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk10.t3.i <- recode (data$gbk10.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
data$gbk11.t3.i <- recode (data$gbk11.t3, '1=7; 2=6; 3=5; 5=3; 6=2; 7=1')
```

```{r}
#Calculating means basic psychological needs

data$gbk.t3.r <- rowMeans (data [c("gbk13.t3", "gbk14.t3", "gbk15.t3",
                                   "gbk16.t3.i", "gbk17.t3.i", "gbk18.t3.i")])   #relatedness satisfaction

data$gbk.t3.a <- rowMeans (data [c("gbk1.t3", "gbk2.t3", "gbk6.t3",
                                   "gbk3.t3.i", "gbk4.t3.i", "gbk5.t3.i")])    #autonomy satisfaction

data$gbk.t3.c <- rowMeans (data [c("gbk9.t3", "gbk12.t3",
                                   "gbk8.t3.i", "gbk10.t3.i", "gbk11.t3.i")])  #competence satisfaction


data$gbk.t3.s <- rowMeans (data [c("gbk13.t3", "gbk14.t3", "gbk15.t3",
                                   "gbk16.t3.i", "gbk17.t3.i", "gbk18.t3.i",
                                   "gbk1.t3", "gbk2.t3", "gbk6.t3",
                                   "gbk3.t3.i", "gbk4.t3.i", "gbk5.t3.i",
                                   "gbk9.t3", "gbk12.t3",
                                   "gbk8.t3.i", "gbk10.t3.i", "gbk11.t3.i")])  #basic needs satisfaction
```

```{r}
#### Sufficiency orientation
#Inverting items

data$so4.t3.i <- recode (data$so4.t3, '1=5; 2=4; 4=2; 5=1')
```

```{r}
#z-standardizing items

data$sv1.t3.z <- scale(data$sv1.t3)
data$sv2.t3.z <- scale(data$sv2.t3)
data$sv3.t3.z <- scale(data$sv3.t3)
data$sv4.t3.z <- scale(data$sv4.t3)
data$sv5.t3.z <- scale(data$sv5.t3)
data$sv6.t3.z <- scale(data$sv6.t3)
data$sv12.t3.z <- scale(data$sv12.t3)
data$sv13.t3.z <- scale(data$sv13.t3)
data$sv14.t3.z <- scale(data$sv14.t3)
data$sv15.t3.z <- scale(data$sv15.t3)
data$sv16.t3.z <- scale(data$sv16.t3)
data$sv17.t3.z <- scale(data$sv17.t3)
data$sv18.t3.z <- scale(data$sv18.t3)

data$so1.t3.z <- scale(data$so1.t3)
data$so2.t3.z <- scale(data$so2.t3)
data$so3.t3.z <- scale(data$so3.t3)
data$so4.t3.i.z <- scale(data$so4.t3.i)
data$so5.t3.z <- scale(data$so5.t3)
data$so6.t3.z <- scale(data$so6.t3)
data$so7.t3.z <- scale(data$so7.t3)
data$so8.t3.z <- scale(data$so8.t3)
data$so9.t3.z <- scale(data$so9.t3)
data$so10.t3.z <- scale(data$so10.t3)
data$so11.t3.z <- scale(data$so11.t3)
data$so12.t3.z <- scale(data$so12.t3)
data$so13.t3.z <- scale(data$so13.t3)
```

```{r}
#Calculating mean sufficiency orientation

data$s.t3 <- rowMeans (data [c("so1.t3.z", "so2.t3.z", "so4.t3.i.z", "so5.t3.z",
                               "so6.t3.z", "so8.t3.z", "so9.t3.z", "so10.t3.z",
                               "so11.t3.z", "so12.t3.z", "so13.t3.z",
                               "sv1.t3.z", "sv2.t3.z", "sv3.t3.z", "sv4.t3.z",
                               "sv5.t3.z", "sv6.t3.z",
                               "sv12.t3.z", "sv13.t3.z", "sv14.t3.z", "sv15.t3.z",
                               "so7.t3.z",
                               "sv16.t3.z", "sv17.t3.z", "sv18.t3.z", "so3.t3.z")])
```


```{r}
#### Self-reflection

data$sr.t3 <- rowMeans (data [c("sr1.t3", "sr2.t3", "sr3.t3", "sr4.t3",
                                "sr5.t3", "sr7.t3")]) 
```

```{r}
#### Standardized scales T3

# Sufficiency orientation
data$s.t3.z <- scale(data [,"s.t3"])

# Subjective well-being
data$swb.t3.z <- scale(data [,"swb.t3"])

# Basic psychological needs
data$gbk.t3.s.z <- scale(data [,"gbk.t3.s"])

# Time affluence
data$t.t3.z <- scale(data [,"t.t3"])

# Self-reflection
data$sr.t3.z <- scale(data [,"sr.t3"])
```


```{r}
### Calculating outliers T3

d.t3 <- filter(data, ok.t3 == 1 & dauer.t3 > 0 & (check.t3 == 4 | is.na(check.t3)))

d.t3.a <- filter(d.t3, s.t3.z <= 2.5 & s.t3.z >= (-2.5)
                & swb.t3.z <= 2.5 & swb.t3.z >= (-2.5) 
                & gbk.t3.s.z <= 2.5 & gbk.t3.s.z >= (-2.5) 
                & t.t3.z <= 2.5 & t.t3.z >= (-2.5)
                & sr.t3.z <= 2.5 & sr.t3.z >= (-2.5)) 
```

```{r}
### Renaming dataset T3

table_fu <- d.t3.a
```


```{r}
## Combining datasets
#Combining T1 and T2

table_pre_post <- full_join(table_pre, table_post, by = c ("case", "bed"))
```

```{r}
#Attaching T3

d <- full_join(table_pre_post, table_fu, by = c ("case", "bed"))
data <- d
```



# Scatterplots
```{r}
pairs(~data$swb.t1+data$swb.t2+data$swb.t3+
       data$t.t1+data$t.t2+data$t.t3+
       data$sr.t1+data$sr.t2+data$sr.t3+
       data$gbk.t1.s+data$gbk.t2.s+data$gbk.t3.s, 
       data$s.t1 +
       data$s.t2 + 
       data$s.t3, data=data,
      main="Scatterplot Matrix")
```

# EFA sufficiency items {.tabset}
```{r}
subset.1 <- data[c("sv1.t1", "sv2.t1", "sv3.t1", "sv4.t1", "sv5.t1",
                   "sv6.t1", "sv12.t1", "sv13.t1", "sv14.t1", "sv15.t1",
                   "sv16.t1", "sv17.t1", "sv18.t1",
                   "so1.t1", "so2.t1", "so3.t1", "so4.t1", "so5.t1",
                   "so6.t1", "so7.t1", "so8.t1", "so9.t1", "so10.t1",
                   "so11.t1", "so12.t1", "so13.t1")] 

```

## Checking data suitability using the Kaiser-Maier-Olkin coeffizient
```{r}
KMO(subset.1)
```

## Simple scree plot
```{r}
VSS.scree (subset.1)
```

## Horn's parallel analysis
```{r}
parallel.1 <- fa.parallel (subset.1, fm="pa", fa = "fa")
```

Eigenvalues of factors
```{r}
parallel.1$fa.values
```

## Factor analysis with fixed number of factors
with oblique rotation
```{r}
fa.pa.promax.1 <- fa(subset.1, 5, fm = "pa", rotate = "Promax")  
print (fa.pa.promax.1, digits = 2, cut = .3, sort = TRUE)       
```

## Visualizing results
```{r}
fa.diagram(fa.pa.promax.1, simple=TRUE, cut=.4, digits=2)
```

# Descriptives {.tabset}
## Age and political orientation
```{r}
subset.sd <- subset (data, select = c(age.t1, age.t2, age.t3, 
                                      pol_orient.t1, pol_orient.t2, pol_orient.t3))

describe (subset.sd)
```

## Gender
```{r}
table (data$gender.t1)
prop.table (table (data$gender.t1))

table (data$gender.t2)
prop.table (table (data$gender.t2))

table (data$gender.t3)
prop.table (table (data$gender.t3))
```

## Education
```{r}
table (data$edu.t1)
prop.table (table (data$edu.t1))

table (data$edu.t2)
prop.table (table (data$edu.t2))

table (data$edu.t3)
prop.table (table (data$edu.t3))
```

## Income
```{r}
table (data$income.t1)
prop.table (table (data$income.t1))

table (data$income.t2)
prop.table (table (data$income.t2))

table (data$income.t3)
prop.table (table (data$income.t3))
```

## Subjective well-being
```{r}
subset.swb <- subset (data, select = c(swb.t1, swb.t2, swb.t3))

describe (subset.swb)
```

## Time affluence
```{r}
subset.t <- subset (data, select = c(t.t1, t.t2, t.t3))

describe (subset.t)
```

## Basic psychological needs
```{r}
subset.gb <- subset (data, select = c(gbk.t1.s, gbk.t1.a, gbk.t1.c, gbk.t1.r,
                                      gbk.t2.s, gbk.t2.a, gbk.t2.c, gbk.t2.r,
                                      gbk.t3.s, gbk.t3.a, gbk.t3.c, gbk.t3.r))

describe (subset.gb)
```

## Sufficiency orientation
```{r}
subset.s <- subset (data, select = c(s.t1, s.t2, s.t3))
describe (subset.s)
```

## Self-reflection
```{r}
subset.sr <- subset (data, select = c(sr.t1, sr.t2, sr.t3))

describe (subset.sr)
```

# Descriptives by group/condition {.tabset}
## N
```{r}
subset.sd <- subset (data, select = c(bed, ok.t1, ok.t2, ok.t3)) 
                           
describe (subset.sd)
describeBy(subset.sd, data$bed, mat = TRUE)
```

## Age and political orientation
```{r}
subset.sd <- subset (data, select = c(age.t1, age.t2, age.t3, 
                                      pol_orient.t1, pol_orient.t2, pol_orient.t3))

describeBy(subset.sd, data$bed, mat = TRUE)
```

## Gender
```{r}
table (data$gender.t1, data$bed)
prop.table(table (data$gender.t1, data$bed))

table (data$gender.t2, data$bed)
prop.table (table (data$gender.t2, data$bed))

table (data$gender.t3, data$bed)
prop.table (table (data$gender.t3, data$bed))
```

## Education
```{r}
table (data$edu.t1, data$bed)
prop.table (table (data$edu.t1, data$bed))

table (data$edu.t2, data$bed)
prop.table (table (data$edu.t2, data$bed))

table (data$edu.t3, data$bed)
prop.table (table (data$edu.t3, data$bed))
```

## Income
```{r}
table (data$income.t1, data$bed)
prop.table (table (data$income.t1, data$bed))

table (data$income.t2, data$bed)
prop.table (table (data$income.t2, data$bed))

table (data$income.t3, data$bed)
prop.table (table (data$income.t3, data$bed))
```

## Subjective well-being
```{r}
subset.swb <- subset (data, select = c(swb.t1, swb.t2, swb.t3))

describeBy(subset.swb, data$bed, mat = TRUE)
```

## Time affluence
```{r}
subset.t <- subset (data, select = c(t.t1, t.t2, t.t3))

describeBy(subset.t, data$bed, mat = TRUE)
```

## Basic psychological needs
```{r}
subset.gb <- subset (data, select = c(gbk.t1.s, gbk.t1.a, gbk.t1.c, gbk.t1.r,
                                      gbk.t2.s, gbk.t2.a, gbk.t2.c, gbk.t2.r,
                                      gbk.t3.s, gbk.t3.a, gbk.t3.c, gbk.t3.r))

describeBy(subset.gb, data$bed, mat = TRUE)
```

## Sufficiency orientation
```{r}
subset.s <- subset (data, select = c(s.t1, s.t2, s.t3))

describeBy(subset.s, data$bed, mat = TRUE)
```

## Self-reflection
```{r}
subset.sr <- subset (data, select = c(sr.t1, sr.t2, sr.t3))

describeBy(subset.sr, data$bed, mat = TRUE)
```

# Reliability {.tabset}
## Subjective well-being {.tabset}
### T1
```{r}
alpha (data[c("swb1.t1", "swb2.t1", "swb3.t1", "swb4.t1", 
              "swb5.t1", "swb6.t1", "swb7.t1.i", "swb8.t1.i",
              "swb9.t1.i", "swb10.t1.i", "swb11.t1.i", "swb12.t1.i")])
```

### T2
```{r}
alpha (data[c("swb1.t2", "swb2.t2", "swb3.t2", "swb4.t2", 
              "swb5.t2", "swb6.t2", "swb7.t2.i", "swb8.t2.i",
              "swb9.t2.i", "swb10.t2.i", "swb11.t2.i", "swb12.t2.i")])   
```

### T3
```{r}
alpha (data[c("swb1.t3", "swb2.t3", "swb3.t3", "swb4.t3", 
              "swb5.t3", "swb6.t3", "swb7.t3.i", "swb8.t3.i",
              "swb9.t3.i", "swb10.t3.i", "swb11.t3.i", "swb12.t3.i")])  
```

## Time affluence {.tabset}
### T1
```{r}
alpha (data[c("t1.t1.i", "t2.t1", "t3.t1.i", "t4.t1",
              "t5.t1", "t6.t1.i", "t7.t1", "t8.t1.i")])
```

### T2
```{r}
alpha (data[c("t1.t2.i", "t2.t2", "t3.t2.i", "t4.t2",
              "t5.t2", "t6.t2.i", "t7.t2", "t8.t2.i")]) 
```

### T3
```{r}
alpha (data[c("t1.t3.i", "t2.t3", "t3.t3.i", "t4.t3",
              "t5.t3", "t6.t3.i", "t7.t3", "t8.t3.i")]) 
```

## Basic psychological needs {.tabset}
### T1
```{r}
alpha (data[c("gbk13.t1", "gbk14.t1", "gbk15.t1",
              "gbk16.t1.i", "gbk17.t1.i", "gbk18.t1.i",
              "gbk1.t1", "gbk2.t1", "gbk6.t1",
              "gbk3.t1.i", "gbk4.t1.i", "gbk5.t1.i",
              "gbk9.t1", "gbk12.t1",
              "gbk10.t1.i", "gbk11.t1.i",
              "gbk8.t1.i")])
```

### T2
```{r}
alpha (data[c("gbk13.t2", "gbk14.t2", "gbk15.t2",
              "gbk16.t2.i", "gbk17.t2.i", "gbk18.t2.i",
              "gbk1.t2", "gbk2.t2", "gbk6.t2",
              "gbk3.t2.i", "gbk4.t2.i", "gbk5.t2.i",
              "gbk9.t2", "gbk12.t2",
              "gbk10.t2.i", "gbk11.t2.i",
              "gbk8.t2.i")])
```

### T3
```{r}
alpha (data[c("gbk13.t3", "gbk14.t3", "gbk15.t3",
              "gbk16.t3.i", "gbk17.t3.i", "gbk18.t3.i",
              "gbk1.t3", "gbk2.t3", "gbk6.t3",
              "gbk3.t3.i", "gbk4.t3.i", "gbk5.t3.i",
              "gbk9.t3", "gbk12.t3",
              "gbk10.t3.i", "gbk11.t3.i",
              "gbk8.t3.i")])
```

## Self-reflection {.tabset}
### T1
```{r}
alpha (data[c("sr1.t1", "sr2.t1", "sr3.t1", "sr4.t1",
              "sr5.t1", "sr7.t1")])                       
```

### T2
```{r}
alpha (data[c("sr1.t2", "sr2.t2", "sr3.t2", "sr4.t2",
              "sr5.t2", "sr7.t2")])                      
```

### T3
```{r}
alpha (data[c("sr1.t3", "sr2.t3", "sr3.t3", "sr4.t3",
              "sr5.t3", "sr7.t3")])                      
```

### Self-reflection all items {.tabset}
#### T1
```{r}
alpha (data[c("sr1.t1", "sr2.t1", "sr3.t1", "sr4.t1",
              "sr5.t1", "sr6.t1", "sr7.t1")])                   
```

#### T2
```{r}
alpha (data[c("sr1.t2", "sr2.t2", "sr3.t2", "sr4.t2",
              "sr5.t2", "sr6.t2", "sr7.t2")])                
```

#### T3
```{r}
 alpha (data[c("sr1.t3", "sr2.t3", "sr3.t3", "sr4.t3",
              "sr5.t3", "sr6.t3", "sr7.t3")])                
```

## Sufficiency orientation {.tabset}
### T1
```{r}
alpha (data [c("so1.t1.z", "so2.t1.z", "so4.t1.i.z", "so5.t1.z",
                               "so6.t1.z", "so8.t1.z", "so9.t1.z", "so10.t1.z",
                               "so11.t1.z", "so12.t1.z", "so13.t1.z",
                               "sv1.t1.z", "sv2.t1.z", "sv3.t1.z", "sv4.t1.z",
                               "sv5.t1.z", "sv6.t1.z",
                               "sv12.t1.z", "sv13.t1.z", "sv14.t1.z", "sv15.t1.z",
                               "so7.t1.z",
                               "sv16.t1.z", "sv17.t1.z", "sv18.t1.z", "so3.t1.z")])
```

### T2
```{r}
alpha (data [c("so1.t2.z", "so2.t2.z", "so4.t2.i.z", "so5.t2.z",
                               "so6.t2.z", "so8.t2.z", "so9.t2.z", "so10.t2.z",
                               "so11.t2.z", "so12.t2.z", "so13.t2.z",
                               "sv1.t2.z", "sv2.t2.z", "sv3.t2.z", "sv4.t2.z",
                               "sv5.t2.z", "sv6.t2.z",
                               "sv12.t2.z", "sv13.t2.z", "sv14.t2.z", "sv15.t2.z",
                               "so7.t2.z",
                               "sv16.t2.z", "sv17.t2.z", "sv18.t2.z", "so3.t2.z")])
```

### T3
```{r}
alpha (data [c("so1.t3.z", "so2.t3.z", "so4.t3.i.z", "so5.t3.z",
                               "so6.t3.z", "so8.t3.z", "so9.t3.z", "so10.t3.z",
                               "so11.t3.z", "so12.t3.z", "so13.t3.z",
                               "sv1.t3.z", "sv2.t3.z", "sv3.t3.z", "sv4.t3.z",
                               "sv5.t3.z", "sv6.t3.z",
                               "sv12.t3.z", "sv13.t3.z", "sv14.t3.z", "sv15.t3.z",
                               "so7.t3.z",
                               "sv16.t3.z", "sv17.t3.z", "sv18.t3.z", "so3.t3.z")])
```


# Reliability by group/condition {.tabset}
## Subjective well-being {.tabset}
### Control group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 0)[c("swb1.t1", "swb2.t1", "swb3.t1", "swb4.t1", 
              "swb5.t1", "swb6.t1", "swb7.t1.i", "swb8.t1.i",
              "swb9.t1.i", "swb10.t1.i", "swb11.t1.i", "swb12.t1.i")])  
```

#### T2
```{r}
alpha (subset(data, bed == 0)[c("swb1.t2", "swb2.t2", "swb3.t2", "swb4.t2", 
              "swb5.t2", "swb6.t2", "swb7.t2.i", "swb8.t2.i",
              "swb9.t2.i", "swb10.t2.i", "swb11.t2.i", "swb12.t2.i")])  
```

#### T3
```{r}
alpha (subset(data, bed == 0)[c("swb1.t3", "swb2.t3", "swb3.t3", "swb4.t3", 
              "swb5.t3", "swb6.t3", "swb7.t3.i", "swb8.t3.i",
              "swb9.t3.i", "swb10.t3.i", "swb11.t3.i", "swb12.t3.i")])  
```

### Intervention group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 1)[c("swb1.t1", "swb2.t1", "swb3.t1", "swb4.t1", 
              "swb5.t1", "swb6.t1", "swb7.t1.i", "swb8.t1.i",
              "swb9.t1.i", "swb10.t1.i", "swb11.t1.i", "swb12.t1.i")])
```

#### T2
```{r}
alpha (subset(data, bed == 1)[c("swb1.t2", "swb2.t2", "swb3.t2", "swb4.t2", 
              "swb5.t2", "swb6.t2", "swb7.t2.i", "swb8.t2.i",
              "swb9.t2.i", "swb10.t2.i", "swb11.t2.i", "swb12.t2.i")])  
```

#### T3
```{r}
alpha (subset(data, bed == 1)[c("swb1.t3", "swb2.t3", "swb3.t3", "swb4.t3", 
              "swb5.t3", "swb6.t3", "swb7.t3.i", "swb8.t3.i",
              "swb9.t3.i", "swb10.t3.i", "swb11.t3.i", "swb12.t3.i")])   
```

## Time affluence  {.tabset}
### Control group  {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 0)[c("t1.t1.i", "t2.t1", "t3.t1.i", "t4.t1",
              "t5.t1", "t6.t1.i", "t7.t1", "t8.t1.i")]) 
```

#### T2
```{r}
alpha (subset(data, bed == 0)[c("t1.t2.i", "t2.t2", "t3.t2.i", "t4.t2",
              "t5.t2", "t6.t2.i", "t7.t2", "t8.t2.i")])  
```

#### T3
```{r}
alpha (subset(data, bed == 0)[c("t1.t3.i", "t2.t3", "t3.t3.i", "t4.t3",
              "t5.t3", "t6.t3.i", "t7.t3", "t8.t3.i")])   
```


### Intervention group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 1)[c("t1.t1.i", "t2.t1", "t3.t1.i", "t4.t1",
              "t5.t1", "t6.t1.i", "t7.t1", "t8.t1.i")])
```

#### T2
```{r}
alpha (subset(data, bed == 1)[c("t1.t2.i", "t2.t2", "t3.t2.i", "t4.t2",
              "t5.t2", "t6.t2.i", "t7.t2", "t8.t2.i")]) 
```

#### T3
```{r}
alpha (subset(data, bed == 1)[c("t1.t3.i", "t2.t3", "t3.t3.i", "t4.t3",
              "t5.t3", "t6.t3.i", "t7.t3", "t8.t3.i")]) 
```

## Basic psychological needs {.tabset}
### Control group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 0)[c("gbk13.t1", "gbk14.t1", "gbk15.t1",
              "gbk16.t1.i", "gbk17.t1.i", "gbk18.t1.i",
              "gbk1.t1", "gbk2.t1", "gbk6.t1",
              "gbk3.t1.i", "gbk4.t1.i", "gbk5.t1.i",
              "gbk9.t1", "gbk12.t1",
              "gbk10.t1.i", "gbk11.t1.i",
              "gbk8.t1.i")])
```

#### T2
```{r}
alpha (subset(data, bed == 0)[c("gbk13.t2", "gbk14.t2", "gbk15.t2",
              "gbk16.t2.i", "gbk17.t2.i", "gbk18.t2.i",
              "gbk1.t2", "gbk2.t2", "gbk6.t2",
              "gbk3.t2.i", "gbk4.t2.i", "gbk5.t2.i",
              "gbk9.t2", "gbk12.t2",
              "gbk10.t2.i", "gbk11.t2.i",
              "gbk8.t2.i")])   
```

#### T3
```{r}
alpha (subset(data, bed == 0)[c("gbk13.t3", "gbk14.t3", "gbk15.t3",
              "gbk16.t3.i", "gbk17.t3.i", "gbk18.t3.i",
              "gbk1.t3", "gbk2.t3", "gbk6.t3",
              "gbk3.t3.i", "gbk4.t3.i", "gbk5.t3.i",
              "gbk9.t3", "gbk12.t3",
              "gbk10.t3.i", "gbk11.t3.i",
              "gbk8.t3.i")])   
```


### Intervention group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 1)[c("gbk13.t1", "gbk14.t1", "gbk15.t1",
              "gbk16.t1.i", "gbk17.t1.i", "gbk18.t1.i",
              "gbk1.t1", "gbk2.t1", "gbk6.t1",
              "gbk3.t1.i", "gbk4.t1.i", "gbk5.t1.i",
              "gbk9.t1", "gbk12.t1",
              "gbk10.t1.i", "gbk11.t1.i",
              "gbk8.t1.i")])  
```

#### T2
```{r}
alpha (subset(data, bed == 1)[c("gbk13.t2", "gbk14.t2", "gbk15.t2",
              "gbk16.t2.i", "gbk17.t2.i", "gbk18.t2.i",
              "gbk1.t2", "gbk2.t2", "gbk6.t2",
              "gbk3.t2.i", "gbk4.t2.i", "gbk5.t2.i",
              "gbk9.t2", "gbk12.t2",
              "gbk10.t2.i", "gbk11.t2.i",
              "gbk8.t2.i")])   
```

#### T3
```{r}
alpha (subset(data, bed == 1)[c("gbk13.t3", "gbk14.t3", "gbk15.t3",
              "gbk16.t3.i", "gbk17.t3.i", "gbk18.t3.i",
              "gbk1.t3", "gbk2.t3", "gbk6.t3",
              "gbk3.t3.i", "gbk4.t3.i", "gbk5.t3.i",
              "gbk9.t3", "gbk12.t3",
              "gbk10.t3.i", "gbk11.t3.i",
              "gbk8.t3.i")])                                               
```

## Self-reflection {.tabset}
### Control group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 0)[c("sr1.t1", "sr2.t1", "sr3.t1", "sr4.t1",
              "sr5.t1", "sr7.t1")])
```

#### T2
```{r}
alpha (subset(data, bed == 0)[c("sr1.t2", "sr2.t2", "sr3.t2", "sr4.t2",
              "sr5.t2", "sr7.t2")])    
```

#### T3
```{r}
alpha (subset(data, bed == 0)[c("sr1.t3", "sr2.t3", "sr3.t3", "sr4.t3",
              "sr5.t3", "sr7.t3")])   
```

### Intervention group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 1)[c("sr1.t1", "sr2.t1", "sr3.t1", "sr4.t1",
              "sr5.t1", "sr7.t1")]) 
```

#### T2
```{r}
alpha (subset(data, bed == 1)[c("sr1.t2", "sr2.t2", "sr3.t2", "sr4.t2",
              "sr5.t2", "sr7.t2")])  
```

#### T3
```{r}
alpha (subset(data, bed == 1)[c("sr1.t3", "sr2.t3", "sr3.t3", "sr4.t3",
              "sr5.t3", "sr7.t3")]) 
```


## Self-reflection all items {.tabset}
### Control group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 0)[c("sr1.t1", "sr2.t1", "sr3.t1", "sr4.t1",
              "sr5.t1", "sr6.t1", "sr7.t1")])    
```

#### T2
```{r}
alpha (subset(data, bed == 0)[c("sr1.t2", "sr2.t2", "sr3.t2", "sr4.t2",
              "sr5.t2", "sr6.t2", "sr7.t2")])    
```

#### T3
```{r}
alpha (subset(data, bed == 0)[c("sr1.t3", "sr2.t3", "sr3.t3", "sr4.t3",
              "sr5.t3", "sr6.t3", "sr7.t3")])       
```

### Intervention group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 1)[c("sr1.t1", "sr2.t1", "sr3.t1", "sr4.t1",
              "sr5.t1", "sr6.t1", "sr7.t1")]) 
```

#### T2
```{r}
alpha (subset(data, bed == 1)[c("sr1.t2", "sr2.t2", "sr3.t2", "sr4.t2",
              "sr5.t2", "sr6.t2", "sr7.t2")])    
```

#### T3
```{r}
alpha (subset(data, bed == 1)[c("sr1.t3", "sr2.t3", "sr3.t3", "sr4.t3",
              "sr5.t3", "sr6.t3", "sr7.t3")])     
```

## Sufficiency orientation {.tabset}
### Control group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 0) [c("so1.t1.z", "so2.t1.z", "so4.t1.i.z", "so5.t1.z",
                               "so6.t1.z", "so8.t1.z", "so9.t1.z", "so10.t1.z",
                               "so11.t1.z", "so12.t1.z", "so13.t1.z",
                               "sv1.t1.z", "sv2.t1.z", "sv3.t1.z", "sv4.t1.z",
                               "sv5.t1.z", "sv6.t1.z",
                               "sv12.t1.z", "sv13.t1.z", "sv14.t1.z", "sv15.t1.z",
                               "so7.t1.z",
                               "sv16.t1.z", "sv17.t1.z", "sv18.t1.z", "so3.t1.z")]) 
```

#### T2
```{r}
alpha (subset(data, bed == 0) [c("so1.t2.z", "so2.t2.z", "so4.t2.i.z", "so5.t2.z",
                               "so6.t2.z", "so8.t2.z", "so9.t2.z", "so10.t2.z",
                               "so11.t2.z", "so12.t2.z", "so13.t2.z",
                               "sv1.t2.z", "sv2.t2.z", "sv3.t2.z", "sv4.t2.z",
                               "sv5.t2.z", "sv6.t2.z",
                               "sv12.t2.z", "sv13.t2.z", "sv14.t2.z", "sv15.t2.z",
                               "so7.t2.z",
                               "sv16.t2.z", "sv17.t2.z", "sv18.t2.z", "so3.t2.z")]) 
```

#### T3
```{r}
alpha (subset(data, bed == 0) [c("so1.t3.z", "so2.t3.z", "so4.t3.i.z", "so5.t3.z",
                               "so6.t3.z", "so8.t3.z", "so9.t3.z", "so10.t3.z",
                               "so11.t3.z", "so12.t3.z", "so13.t3.z",
                               "sv1.t3.z", "sv2.t3.z", "sv3.t3.z", "sv4.t3.z",
                               "sv5.t3.z", "sv6.t3.z",
                               "sv12.t3.z", "sv13.t3.z", "sv14.t3.z", "sv15.t3.z",
                               "so7.t3.z",
                               "sv16.t3.z", "sv17.t3.z", "sv18.t3.z", "so3.t3.z")])
```

### Intervention group {.tabset}
#### T1
```{r}
alpha (subset(data, bed == 1) [c("so1.t1.z", "so2.t1.z", "so4.t1.i.z", "so5.t1.z",
                               "so6.t1.z", "so8.t1.z", "so9.t1.z", "so10.t1.z",
                               "so11.t1.z", "so12.t1.z", "so13.t1.z",
                               "sv1.t1.z", "sv2.t1.z", "sv3.t1.z", "sv4.t1.z",
                               "sv5.t1.z", "sv6.t1.z",
                               "sv12.t1.z", "sv13.t1.z", "sv14.t1.z", "sv15.t1.z",
                               "so7.t1.z",
                               "sv16.t1.z", "sv17.t1.z", "sv18.t1.z", "so3.t1.z")]) 
```

#### T2
```{r}
alpha (subset(data, bed == 1) [c("so1.t2.z", "so2.t2.z", "so4.t2.i.z", "so5.t2.z",
                               "so6.t2.z", "so8.t2.z", "so9.t2.z", "so10.t2.z",
                               "so11.t2.z", "so12.t2.z", "so13.t2.z",
                               "sv1.t2.z", "sv2.t2.z", "sv3.t2.z", "sv4.t2.z",
                               "sv5.t2.z", "sv6.t2.z",
                               "sv12.t2.z", "sv13.t2.z", "sv14.t2.z", "sv15.t2.z",
                               "so7.t2.z",
                               "sv16.t2.z", "sv17.t2.z", "sv18.t2.z", "so3.t2.z")]) 
```

#### T3
```{r}
alpha (subset(data, bed == 1) [c("so1.t3.z", "so2.t3.z", "so4.t3.i.z", "so5.t3.z",
                               "so6.t3.z", "so8.t3.z", "so9.t3.z", "so10.t3.z",
                               "so11.t3.z", "so12.t3.z", "so13.t3.z",
                               "sv1.t3.z", "sv2.t3.z", "sv3.t3.z", "sv4.t3.z",
                               "sv5.t3.z", "sv6.t3.z",
                               "sv12.t3.z", "sv13.t3.z", "sv14.t3.z", "sv15.t3.z",
                               "so7.t3.z",
                               "sv16.t3.z", "sv17.t3.z", "sv18.t3.z", "so3.t3.z")]) 
```

# Correlations
```{r}
corr.test (data[,c("age.t1", "age.t2", "age.t3", 
                    "pol_orient.t1", "pol_orient.t2", "pol_orient.t3",
                    "swb.t1", "swb.t2", "swb.t3",
                    "t.t1", "t.t2", "t.t3",
                    "gbk.t1.s", 
                    "gbk.t2.s",
                    "gbk.t3.s",
                    "s.t1",
                    "s.t2",
                    "s.t3",
                    "sr.t1", "sr.t2", "sr.t3")], 
           method = "spearman")
```

```{r}
data.ci <-  cor.ci(data [,c("age.t1", "age.t2", "age.t3", 
                            "pol_orient.t1", "pol_orient.t2", "pol_orient.t3",
                            "swb.t1", "swb.t2", "swb.t3",
                            "t.t1", "t.t2", "t.t3",
                            "gbk.t1.s", 
                            "gbk.t2.s",
                            "gbk.t3.s",
                            "s.t1",
                            "s.t2",
                            "s.t3",
                            "sr.t1", "sr.t2", "sr.t3")])
```

```{r}
ci <- cor.plot.upperLowerCi(data.ci)
```

Confidence intervals in matrix form
```{r}
ci  
```

# H1: Repeated measures ANOVA {.tabset}

## Within Factors: time, person; between factor: condition {.tabset}
### Preparations
```{r}
#### Packages ####
library(psych)
library(car)
library(gplots)
library(multcomp)
library(effects)
library(ez)
library(sciplot)
library(reshape)
library(ggplot2)
library(ggpubr)
library(magrittr)
library(rstatix)
library(ggpubr)

Analysis1 <- data
myvars.s <- c("s.t1", "s.t2", "s.t3", "case", "bed")

data.anova <- Analysis1[myvars.s]

data.anova.s <- na.omit(data.anova) 

data.anova.s <- data.anova.s %>%
  gather(key = "Time", value = "Sufficiency", s.t1, s.t2, s.t3) %>%
  convert_as_factor(case, Time)

names(data.anova.s) <- c("Case", "Condition", "Time", "Sufficiency")

data.anova.s$Condition <- factor(data.anova.s$Condition, labels = c("Control", "Experimental"))
data.anova.s$Time <- factor(data.anova.s$Time, labels = c("T1", "T2", "T3"))
```

Summary statistics
```{r}
data.anova.s %>%
  group_by(Condition, Time) %>%
  get_summary_stats(Sufficiency, type = "mean_sd")

bxp <- ggboxplot(
  data.anova.s, x = "Time", y = "Sufficiency",
  color = "Condition", palette = "jco"
)
bxp
```

Outliers
```{r}
data.anova.s %>%
  group_by(Condition, Time) %>%
  identify_outliers(Sufficiency) 
```

Assumptions
```{r}
data.anova.s %>%
  group_by(Condition, Time) %>%
  shapiro_test(Sufficiency) 

ggqqplot(data.anova.s, "Sufficiency", ggtheme = theme_bw()) +
  facet_grid(Time ~ Condition, labeller = "label_both")

data.anova.s %>%
  group_by(Time) %>%
  levene_test(Sufficiency ~ Condition) 

box_m(data.anova.s[, "Sufficiency", drop = FALSE], data.anova.s$Condition) 
```

### Two-way mixed ANOVA
```{r}
res.aov.s <- anova_test(
  data = data.anova.s, dv = Sufficiency, wid = Case,
  between = Condition, within = Time
)
get_anova_table(res.aov.s)
```

### Pairwise comparisons
Timepoints as independent Variable
```{r}
data.anova.s%>%
  pairwise_t_test(
    Sufficiency ~ Time, paired = TRUE, 
    p.adjust.method = "bonferroni"
  )
```

Condition as independent Variable
```{r}
data.anova.s %>%
  pairwise_t_test(
    Sufficiency ~ Condition, 
    p.adjust.method = "bonferroni"
  )
```

Effect of group at each time point (within subject effects)
```{r}
one.way.s <- data.anova.s %>%
  group_by(Time) %>%
  anova_test(dv = Sufficiency, wid = Case, between = Condition) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
one.way.s
```

Pairwise comparisons between group levels
```{r}
pwc <- data.anova.s %>%
  group_by(Time) %>%
  pairwise_t_test(Sufficiency ~ Condition, p.adjust.method = "bonferroni")
pwc
```

Effect of time at each level of exercises group
```{r}
one.way.s.2 <- data.anova.s %>%
  group_by(Condition) %>%
  anova_test(dv = Sufficiency, wid = Case, within = Time) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
one.way.s.2
```

Pairwise comparisons between time points at each group levels
```{r}
pwc2 <- data.anova.s %>%
  group_by(Condition) %>%
  pairwise_t_test(
    Sufficiency ~ Time, paired = TRUE, 
    p.adjust.method = "bonferroni"
  )  
pwc2
```

### Visualizations
Boxplots with p-values
```{r}
pwc <- pwc %>% add_xy_position(x = "Time")
pwc.filtered <- pwc %>% filter(Time != "T1")
bxp + 
  stat_pvalue_manual(pwc.filtered, tip.length = 0, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.aov.s, detailed = TRUE),
    caption = get_pwc_label(pwc)
  )
```

Graph displaying both groups 
```{r}
Anovaplot.s <- ggline(data.anova.s, "Time", "Sufficiency", add = "mean_se",
       linetype = "Condition", shape = "Condition", color = "Condition", palette = c("#00AFBB", "#E7B800"), font.label = list(size = 8, color = "black"))

Anovaplot.s

ggsave(Anovaplot.s, file="Anovaplot.png", width = 10,
  height = 7, units = "cm", dpi = 300)
```

## Manipulation check: Self-reflection x time ANOVA {.tabset}
### Preparations
```{r}
attach(Analysis1)
myvars.sr <- c("sr.t1", "sr.t2", "sr.t3", "case", "bed")
data.anova.sr <- Analysis1[myvars.sr]

data.anova.sr <- na.omit(data.anova.sr) 

data.anova.sr <- data.anova.sr %>%
  gather(key = "Time", value = "Reflection", sr.t1, sr.t2, sr.t3) %>%
  convert_as_factor(case, Time)

names(data.anova.sr) <- c("Case", "Condition", "Time", "Reflection")

data.anova.sr$Condition <- factor(data.anova.sr$Condition, labels = c("Control", "Experimental"))
data.anova.sr$Time <- factor(data.anova.sr$Time, labels = c("T1", "T2", "T3"))
```

Summary statistics
```{r}
data.anova.sr %>%
  group_by(Condition, Time) %>%
  get_summary_stats(Reflection, type = "mean_sd")

bxp <- ggboxplot(
  data.anova.sr, x = "Time", y = "Reflection",
  color = "Condition", palette = "jco"
)
bxp
```

Outliers
```{r}
data.anova.sr %>%
  group_by(Condition, Time) %>%
  identify_outliers(Reflection) 
```

Assumptions
```{r}
data.anova.sr %>%
  group_by(Condition, Time) %>%
  shapiro_test(`Reflection`) 

ggqqplot(data.anova.sr, "Reflection", ggtheme = theme_bw()) +
  facet_grid(Time ~ Condition, labeller = "label_both")

data.anova.sr %>%
  group_by(Time) %>%
  levene_test(Reflection ~ Condition) 

box_m(data.anova.sr[, "Reflection", drop = FALSE], data.anova.sr$Condition) 
```

### Repeated measures ANOVA 
```{r}
res.aov.sr <- anova_test(
  data = data.anova.sr, dv = Reflection, wid = Case,
  between = Condition, within = Time
)
get_anova_table(res.aov.sr)
```

### Pairwise comparisons
Timepoints as independent variable
```{r}
data.anova.sr%>%
  pairwise_t_test(
    Reflection ~ Time, paired = TRUE, 
    p.adjust.method = "bonferroni")
```

Condition as independent Variable
```{r}
data.anova.sr %>%
  pairwise_t_test(
    Reflection ~ Condition, 
    p.adjust.method = "bonferroni")
```

Effect of group at each time point (within subject effects)
```{r}
one.way.sr <- data.anova.sr %>%
  group_by(Time) %>%
  anova_test(dv = Reflection, wid = Case, between = Condition) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
one.way.sr
```

Pairwise comparisons between group levels
```{r}
pwc <- data.anova.sr %>%
  group_by(Time) %>%
  pairwise_t_test(Reflection ~ Condition, p.adjust.method = "bonferroni")
pwc
```

Effect of time at each level of exercises group
```{r}
one.way.sr.2 <- data.anova.sr %>%
  group_by(Condition) %>%
  anova_test(dv = Reflection, wid = Case, within = Time) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
one.way.sr.2
```

Pairwise comparisons between time points at each group levels
```{r}
pwc2 <- data.anova.sr %>%
  group_by(Condition) %>%
  pairwise_t_test(
    Reflection ~ Time, paired = TRUE, 
    p.adjust.method = "bonferroni"
  )  
pwc2
```

### Visualizations
Boxplots with p-values
```{r}
pwc <- pwc %>% add_xy_position(x = "Time")
pwc.filtered <- pwc %>% filter(Time != "T1")
bxp + 
  stat_pvalue_manual(pwc.filtered, tip.length = 0, hide.ns = TRUE) +
  labs(
    subtitle = get_test_label(res.aov.sr, detailed = TRUE),
    caption = get_pwc_label(pwc)
  )
```

Graph displaying both groups
```{r}
ggline(data.anova.sr, "Time", "Reflection", add = "mean_se",
       linetype = "Condition", shape = "Condition", color = "Condition", palette = c("#00AFBB", "#E7B800"), font.label = list(size = 8, color = "black"))
```

# H2: Basic psychological need satisfaction is positively associated with sufficiency
```{r}
corr.test (data[,c("gbk.t1.s", "gbk.t1.a", "gbk.t1.c", "gbk.t1.r",
                   "gbk.t2.s", "gbk.t2.a", "gbk.t2.c", "gbk.t2.r",
                   "gbk.t3.s", "gbk.t3.a", "gbk.t3.c", "gbk.t3.r",
                   "s.t1", "s.t2", "s.t3")], 
           method = "spearman")
```

```{r}
data.ci <-  cor.ci(data [,c("gbk.t1.s", "gbk.t1.a", "gbk.t1.c", "gbk.t1.r",
                   "gbk.t2.s", "gbk.t2.a", "gbk.t2.c", "gbk.t2.r",
                   "gbk.t3.s", "gbk.t3.a", "gbk.t3.c", "gbk.t3.r",
                   "s.t1", "s.t2", "s.t3")])
```

```{r}
ci <- cor.plot.upperLowerCi(data.ci)
```

Confidence intervals in matrix form
```{r}
ci  
```

# H4: Self-reflection is positively associated with sufficiency
```{r}
corr.test (data[,c("s.t1", "s.t2", "s.t3",
                   "sr.t1", "sr.t2", "sr.t3")], 
           method = "spearman")
```

```{r}
data.ci <-  cor.ci(data [,c("s.t1", "s.t2", "s.t3",
                            "sr.t1", "sr.t2", "sr.t3")])
```

```{r}
ci <- cor.plot.upperLowerCi(data.ci)
```

Confidence intervals in matrix form
```{r}
ci  
```

# H3 & H5: Mediation analysis basic psychological needs and self-reflection {.tabset}
```{r}
#Load packages

library(lavaan)
library(ggraph)
library(knitr)
library(ggplot2)
library(semPlot)
library(MVN)
```

## Assumptions T1
```{r}
#Create data frame with sem.t1 items

data.sem.t1 = data.frame(data$s.t1, data$sr.t1, data$gbk.t1.s, data$age.t1,
                         data$pol_orient.t1)
```

```{r}
#Inspect data visually

mvn(data = data.sem.t1, mvnTest = "royston", univariatePlot = "histogram")
```

```{r}
#Check for overall multivariate normality (Doornik-Hansen's test) 

result <- mvn(data = data.sem.t1, mvnTest = "dh")
result$multivariateNormality
```

## Assumptions T2
```{r}
#Create data frame with sem.t2 items

data.sem.t2 = data.frame(data$s.t2, data$sr.t2, data$gbk.t2.s, data$age.t2,
                         data$pol_orient.t2, data$s.t1)
```

```{r}
#Inspect data visually

mvn(data = data.sem.t2, mvnTest = "royston", univariatePlot = "histogram") 
```

```{r}
#Check for overall multivariate normality (Doornik-Hansen's test) 

result <- mvn(data = data.sem.t2, mvnTest = "dh")
result$multivariateNormality
```

## Assumptions T3
```{r}
#Create data frame with sem.t3 items

data.sem.t3 = data.frame(data$s.t3, data$sr.t3, data$gbk.t3.s, data$age.t3,
                         data$pol_orient.t3, data$s.t1, data$s.t2)
```

```{r}
#Inspect data visually

mvn(data = data.sem.t3, mvnTest = "royston", univariatePlot = "histogram") 
```

```{r}
#Check for overall multivariate normality (Doornik-Hansen's test) 

result <- mvn(data = data.sem.t3, mvnTest = "dh")
result$multivariateNormality
```

## T1
```{r}
H23.k.t1 <- 's.t1 ~ sr.t1 + gbk.t1.s + age.t1 + gender.t1.d + pol_orient.t1
             gbk.t1.s ~ sr.t1 + age.t1 + gender.t1.d + pol_orient.t1
             sr.t1 ~ age.t1 + gender.t1.d + pol_orient.t1'

fit.H23.k.t1 <- sem(H23.k.t1, data=data,  estimator = "MLM")
summary(fit.H23.k.t1, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
```

Modification indices
```{r}
mod_ind.H23.k.t1 <- modificationindices(fit.H23.k.t1)

head(mod_ind.H23.k.t1[order(mod_ind.H23.k.t1$mi, decreasing=TRUE), ], 10)        

subset(mod_ind.H23.k.t1[order(mod_ind.H23.k.t1$mi, decreasing=TRUE), ], mi > 5)  
```

Variance-Covariance-Matrix
```{r}
inspect(fit.H23.k.t1, "sampstat")$cov        #empircal
fitted(fit.H23.k.t1)$cov                     #model-implicated
```

Standardized residuals
```{r}
cov_table.H23.k.t1 <- resid(fit.H23.k.t1, type="standardized")$cov

cov_table.H23.k.t1[upper.tri(cov_table.H23.k.t1)] <- NA    
diag(cov_table.H23.k.t1) <- NA                    

kable(cov_table.H23.k.t1, digits=2)              
```

## T2
```{r}
H23.k.t2 <- 's.t2 ~ bed + sr.t2 + gbk.t2.s + s.t1 + age.t2 + gender.t2.d + pol_orient.t2
             gbk.t2.s ~ bed + sr.t2 + age.t2 + gender.t2.d + pol_orient.t2
                sr.t2 ~ bed + age.t2 + gender.t2.d + pol_orient.t2'

fit.H23.k.t2 <- sem(H23.k.t2, data=data, estimator = "MLM")
summary(fit.H23.k.t2, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
```

Modification indices
```{r}
mod_ind.H23.k.t2 <- modificationindices(fit.H23.k.t2)

head(mod_ind.H23.k.t2[order(mod_ind.H23.k.t2$mi, decreasing=TRUE), ], 10)        

subset(mod_ind.H23.k.t2[order(mod_ind.H23.k.t2$mi, decreasing=TRUE), ], mi > 5)  
```

Variance-Covariance-Matrix
```{r}
inspect(fit.H23.k.t2, "sampstat")$cov        #empirical
fitted(fit.H23.k.t2)$cov                     #model-implicated
```

Standardized residuals
```{r}
cov_table.H23.k.t2 <- resid(fit.H23.k.t2, type="standardized")$cov

cov_table.H23.k.t2[upper.tri(cov_table.H23.k.t2)] <- NA    
diag(cov_table.H23.k.t2) <- NA                  

kable(cov_table.H23.k.t2, digits=2)             
```

## T3
```{r}
H23.k.t3 <- 's.t3 ~ bed + sr.t3 + gbk.t3.s + s.t1 + s.t2 + age.t3 + gender.t3.d + pol_orient.t3
             gbk.t3.s ~ bed + sr.t3 + age.t3 + gender.t3.d + pol_orient.t3
             sr.t3 ~ bed + age.t3 + gender.t3.d + pol_orient.t3'

fit.H23.k.t3 <- sem(H23.k.t3, data=data, estimator = "MLM")
summary(fit.H23.k.t3, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
```

Modification indices
```{r}
mod_ind.H23.k.t3 <- modificationindices(fit.H23.k.t3)

head(mod_ind.H23.k.t3[order(mod_ind.H23.k.t3$mi, decreasing=TRUE), ], 10)       

subset(mod_ind.H23.k.t3[order(mod_ind.H23.k.t3$mi, decreasing=TRUE), ], mi > 5) 
```

Variance-Covariance-Matrix
```{r}
inspect(fit.H23.k.t3, "sampstat")$cov        #empirical
fitted(fit.H23.k.t3)$cov                     #model-implicated
```

Standardized residuals
```{r}
cov_table.H23.k.t3 <- resid(fit.H23.k.t3, type="standardized")$cov

cov_table.H23.k.t3[upper.tri(cov_table.H23.k.t3)] <- NA    
diag(cov_table.H23.k.t3) <- NA                    

kable(cov_table.H23.k.t3, digits=2)              
```

## Splitting overall needs into autonomy and competence {.tabset}
### Assumptions T1 AC
```{r}
#Create data frame with sem.t1 items

data.sem.t1 = data.frame(data$s.t1, data$sr.t1, data$gbk.t1.a, data$gbk.t1.c, data$age.t1,
                         data$pol_orient.t1)
```

```{r}
#Inspect data visually

mvn(data = data.sem.t1, mvnTest = "royston", univariatePlot = "histogram") 
```

```{r}
#Check for overall multivariate normality (Doornik-Hansen's test) 

result <- mvn(data = data.sem.t1, mvnTest = "dh")
result$multivariateNormality
```

### Assumptions T2 AC
```{r}
#Create data frame with sem.t2 items

data.sem.t2 = data.frame(data$s.t2, data$sr.t2, data$gbk.t2.a, data$gbk.t2.c, data$age.t2,
                         data$pol_orient.t2, data$s.t1)
```

```{r}
#Inspect data visually

mvn(data = data.sem.t2, mvnTest = "royston", univariatePlot = "histogram") 
```

```{r}
#Check for overall multivariate normality (Doornik-Hansen's test) 

result <- mvn(data = data.sem.t2, mvnTest = "dh")
result$multivariateNormality
```

### Assumptions T3 AC
```{r}
#Create data frame with sem.t3 items

data.sem.t3 = data.frame(data$s.t3, data$sr.t3, data$gbk.t3.a, data$gbk.t3.c, data$age.t3,
                         data$pol_orient.t3, data$s.t1, data$s.t2)
```

```{r}
#Inspect data visually

mvn(data = data.sem.t3, mvnTest = "royston", univariatePlot = "histogram")
```

```{r}
#Check for overall multivariate normality (Doornik-Hansen's test) 

result <- mvn(data = data.sem.t3, mvnTest = "dh")
result$multivariateNormality
```

### T1 AC
```{r}
H23.k.t1 <- 's.t1 ~ sr.t1 + gbk.t1.a + gbk.t1.c + age.t1 + gender.t1.d + pol_orient.t1
             gbk.t1.a ~ sr.t1 + age.t1 + gender.t1.d + pol_orient.t1
             gbk.t1.c ~ sr.t1 + age.t1 + gender.t1.d + pol_orient.t1
             sr.t1 ~ age.t1 + gender.t1.d + pol_orient.t1'

fit.H23.k.t1 <- sem(H23.k.t1, data=data,  estimator = "MLM")
summary(fit.H23.k.t1, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
```

Modification indices
```{r}
mod_ind.H23.k.t1 <- modificationindices(fit.H23.k.t1)

head(mod_ind.H23.k.t1[order(mod_ind.H23.k.t1$mi, decreasing=TRUE), ], 10)    

subset(mod_ind.H23.k.t1[order(mod_ind.H23.k.t1$mi, decreasing=TRUE), ], mi > 5) 
```

Variance-Covariance-Matrix
```{r}
inspect(fit.H23.k.t1, "sampstat")$cov        #empirical
fitted(fit.H23.k.t1)$cov                     #model-implicated
```

Standardized residuals
```{r}
cov_table.H23.k.t1 <- resid(fit.H23.k.t1, type="standardized")$cov

cov_table.H23.k.t1[upper.tri(cov_table.H23.k.t1)] <- NA   
diag(cov_table.H23.k.t1) <- NA                 

kable(cov_table.H23.k.t1, digits=2)             
```

### T2 AC
```{r}
H23.k.t2 <- 's.t2 ~ bed + sr.t2 + gbk.t2.a + gbk.t2.c + s.t1 + age.t2 + gender.t2.d + pol_orient.t2
             gbk.t2.a ~ bed + sr.t2 + age.t2 + gender.t2.d + pol_orient.t2
             gbk.t2.c ~ bed + sr.t2 + age.t2 + gender.t2.d + pol_orient.t2
             sr.t2 ~ bed + age.t2 + gender.t2.d + pol_orient.t2'

fit.H23.k.t2 <- sem(H23.k.t2, data=data, estimator = "MLM")
summary(fit.H23.k.t2, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
```

Modification indices
```{r}
mod_ind.H23.k.t2 <- modificationindices(fit.H23.k.t2)

head(mod_ind.H23.k.t2[order(mod_ind.H23.k.t2$mi, decreasing=TRUE), ], 10)     

subset(mod_ind.H23.k.t2[order(mod_ind.H23.k.t2$mi, decreasing=TRUE), ], mi > 5) 
```

Variance-Covariance-Matrix
```{r}
inspect(fit.H23.k.t2, "sampstat")$cov        #empirical
fitted(fit.H23.k.t2)$cov                     #model-implicated
```

Standardized residuals
```{r}
cov_table.H23.k.t2 <- resid(fit.H23.k.t2, type="standardized")$cov

cov_table.H23.k.t2[upper.tri(cov_table.H23.k.t2)] <- NA    
diag(cov_table.H23.k.t2) <- NA                    

kable(cov_table.H23.k.t2, digits=2)              
```

### T3 AC
```{r}
H23.k.t3 <- 's.t3 ~ bed + sr.t3 + gbk.t3.a + gbk.t3.c + s.t1 + s.t2 + age.t3 + gender.t3.d + pol_orient.t3
             gbk.t3.a ~ bed + sr.t3 + age.t3 + gender.t3.d + pol_orient.t3
             gbk.t3.c ~ bed + sr.t3 + age.t3 + gender.t3.d + pol_orient.t3
             sr.t3 ~ bed + age.t3 + gender.t3.d + pol_orient.t3'

fit.H23.k.t3 <- sem(H23.k.t3, data=data, estimator = "MLM")
summary(fit.H23.k.t3, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
```

Modification indices
```{r}
mod_ind.H23.k.t3 <- modificationindices(fit.H23.k.t3)

head(mod_ind.H23.k.t3[order(mod_ind.H23.k.t3$mi, decreasing=TRUE), ], 10)   

subset(mod_ind.H23.k.t3[order(mod_ind.H23.k.t3$mi, decreasing=TRUE), ], mi > 5) 
```

Variance-Covariance-Matrix
```{r}
inspect(fit.H23.k.t3, "sampstat")$cov        #empirical
fitted(fit.H23.k.t3)$cov                     #model-implicated
```

Standardized residuals
```{r}
cov_table.H23.k.t3 <- resid(fit.H23.k.t3, type="standardized")$cov

cov_table.H23.k.t3[upper.tri(cov_table.H23.k.t3)] <- NA   
diag(cov_table.H23.k.t3) <- NA                   

kable(cov_table.H23.k.t3, digits=2)              
```


# H6: Sufficiency orientation predicts subjective well-being {.tabset}
```{r}
#Load packages

library(psych)
library(lm.beta)
library(VIF)
```

## Correlations
```{r}
corr.test (data[,c("swb.t1", "swb.t2", "swb.t3",
                   "s.t1", "s.t2", "s.t3")], 
           method = "spearman")
```

```{r}
data.ci <-  cor.ci(data [,c("swb.t1", "swb.t2", "swb.t3",
                            "s.t1", "s.t2", "s.t3")])
```

```{r}
ci <- cor.plot.upperLowerCi(data.ci)  
```

Confidence intervals in matrix form
```{r}
ci
```

## Regressions T1 {.tabset}
### Step 1
```{r}
Regression.swb.k <- lm(swb.t1 ~ age.t1 + gender.t1.d + pol_orient.t1, data = data)                
summary(Regression.swb.k)
lm.beta(Regression.swb.k)
confint(lm.beta(Regression.swb.k), level = 0.95)


res.lm <- residuals(Regression.swb.k)
describe (res.lm)
shapiro.test(res.lm)

dwt(lm(swb.t1 ~ age.t1 + gender.t1.d + pol_orient.t1, data = data))

method=c("resample","normal")

par(mfrow = c(2, 2)) 
plot(Regression.swb.k)       
par(mfrow = c(1, 1)) 
car::vif(Regression.swb.k) 

```

### Step 2
```{r}
Regression.swb.k2 <- lm(swb.t1 ~ age.t1 + gender.t1.d + pol_orient.t1 + s.t1, data = data)   
summary(Regression.swb.k2)
lm.beta(Regression.swb.k2)
confint(lm.beta(Regression.swb.k2), level = 0.95)

res.lm <- residuals(Regression.swb.k2) 
describe (res.lm)
shapiro.test(res.lm)

dwt(lm(swb.t1 ~ age.t1 + gender.t1.d + pol_orient.t1 + s.t1, data = data))


par(mfrow = c(2, 2)) 
plot(Regression.swb.k2)   
par(mfrow = c(1, 1)) 
car::vif(Regression.swb.k2)
```

### Comparing models
```{r}
anova(Regression.swb.k, Regression.swb.k2)
```

## Regressions T2 {.tabset}
### Step 1
```{r}
Regression.swb.k.t2 <- lm(swb.t2 ~ age.t2 + gender.t2.d + pol_orient.t2, data = data)                
summary(Regression.swb.k.t2)
lm.beta(Regression.swb.k.t2)
confint(lm.beta(Regression.swb.k.t2), level = 0.95)

res.lm <- residuals(Regression.swb.k.t2)
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(swb.t2 ~ age.t2 + gender.t2.d + pol_orient.t2, data = data))

par(mfrow = c(2, 2)) 
plot(Regression.swb.k.t2)    
par(mfrow = c(1, 1)) 
car::vif(Regression.swb.k.t2)
```

### Step 2
```{r}
Regression.swb.k2.t2 <- lm(swb.t2 ~ age.t2 + gender.t2.d + pol_orient.t2 + s.t2, data = data)   
summary(Regression.swb.k2.t2)
lm.beta(Regression.swb.k2.t2)
confint(lm.beta(Regression.swb.k2.t2), level = 0.95)

res.lm <- residuals(Regression.swb.k2.t2) 
describe (res.lm)
shapiro.test(res.lm) 
dwt(lm(swb.t2 ~ age.t2 + gender.t2.d + pol_orient.t2 + s.t2, data = data))


par(mfrow = c(2, 2)) 
plot(Regression.swb.k2.t2)      
par(mfrow = c(1, 1))  
car::vif(Regression.swb.k2.t2) 
```

### Comparing models
```{r}
anova(Regression.swb.k.t2, Regression.swb.k2.t2)
```

## Regressions T3 {.tabset}
### Step 1
```{r}
Regression.swb.k.t3 <- lm(swb.t3 ~ age.t3 + gender.t3.d + pol_orient.t3, data = data)                
summary(Regression.swb.k.t3)
lm.beta(Regression.swb.k.t3)
confint(lm.beta(Regression.swb.k.t3), level = 0.95)

res.lm <- residuals(Regression.swb.k.t3)
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(swb.t3 ~ age.t3 + gender.t3.d + pol_orient.t3, data = data))


par(mfrow = c(2, 2)) 
plot(Regression.swb.k.t3)       
par(mfrow = c(1, 1)) 
car::vif(Regression.swb.k.t3)
```

### Step 2
```{r}
Regression.swb.k2.t3 <- lm(swb.t3 ~ age.t3 + gender.t3.d + pol_orient.t3 + s.t3, data = data)   
summary(Regression.swb.k2.t3)
lm.beta(Regression.swb.k2.t3)
confint(lm.beta(Regression.swb.k2.t3), level = 0.95)


res.lm <- residuals(Regression.swb.k2.t3) 

describe (res.lm)
shapiro.test(res.lm)
dwt(lm(swb.t3 ~ age.t3 + gender.t3.d + pol_orient.t3 + s.t3, data = data))

par(mfrow = c(2, 2)) 
plot(Regression.swb.k2.t3)     
par(mfrow = c(1, 1)) 
car::vif(Regression.swb.k2.t3) 
```

### Comparing models
```{r}
anova(Regression.swb.k.t3, Regression.swb.k2.t3)
```

# H7: Moderation analysis time affluence predicts sufficiency orientation {.tabset}
## Correlations
```{r}
corr.test (data[,c("t.t1", "t.t2", "t.t3",
                   "s.t1", "s.t2", "s.t3")], 
           method = "spearman")
```

```{r}
data.ci <-  cor.ci(data [,c("t.t1", "t.t2", "t.t3",
                            "s.t1", "s.t2", "s.t3")])
```

```{r}
ci <- cor.plot.upperLowerCi(data.ci)  
```

Confidence intervals in matrix form
```{r}
ci
```

## T1 {.tabset}
### Step 1
```{r}
Regression.s.k <- lm(s.t1 ~ age.t1 + gender.t1.d + pol_orient.t1, data = data)                
summary(Regression.s.k)
lm.beta(Regression.s.k)
confint(lm.beta(Regression.s.k), level = 0.95)

res.lm <- residuals(Regression.s.k) 
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t1 ~ age.t1 + gender.t1.d + pol_orient.t1, data = data))


par(mfrow = c(2, 2))  
plot(Regression.s.k)     
par(mfrow = c(1, 1)) 
car::vif(Regression.s.k)
```

### Step 2
```{r}
Regression.s.k2 <- lm(s.t1 ~ age.t1 + gender.t1.d + pol_orient.t1 + t.t1, data = data)   
summary(Regression.s.k2)
lm.beta(Regression.s.k2)
confint(lm.beta(Regression.s.k2), level = 0.95)

res.lm <- residuals(Regression.s.k2) 
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t1 ~ age.t1 + gender.t1.d + pol_orient.t1 + t.t1, data = data))

par(mfrow = c(2, 2))  
plot(Regression.s.k2)   
par(mfrow = c(1, 1))  

car::vif(Regression.s.k2) 
```

### Comparing models
```{r}
anova(Regression.s.k, Regression.s.k2)
```

## T2 {.tabset}
### Step 1
```{r}
Regression.s.k.t2 <- lm(s.t2 ~ age.t2 + gender.t2.d + pol_orient.t2, data = data)                
summary(Regression.s.k.t2)
lm.beta(Regression.s.k.t2)
confint(lm.beta(Regression.s.k.t2), level = 0.95)

res.lm <- residuals(Regression.s.k.t2)
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t2 ~ s.t1 + age.t2 + gender.t2.d + pol_orient.t2, data = data))



par(mfrow = c(2, 2)) 
plot(Regression.s.k.t2)      
par(mfrow = c(1, 1))

car::vif(Regression.s.k.t2) 
```

### Step 2
```{r}
Regression.s.k2.t2 <- lm(s.t2 ~ age.t2 + gender.t2.d + pol_orient.t2 + bed + t.t2, data = data)   
summary(Regression.s.k2.t2)
lm.beta(Regression.s.k2.t2)
confint(lm.beta(Regression.s.k2.t2), level = 0.95)

res.lm <- residuals(Regression.s.k2.t2)
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t2 ~ s.t1 + age.t2 + gender.t2.d + pol_orient.t2 + bed + t.t2, data = data))



par(mfrow = c(2, 2)) 
plot(Regression.s.k2.t2)       
par(mfrow = c(1, 1))  

car::vif(Regression.s.k2.t2)
```

### Step 3
```{r}
Regression.s.k3.t2 <- lm(s.t2 ~ age.t2 + gender.t2.d + pol_orient.t2 + bed*t.t2, data = data)     
summary(Regression.s.k3.t2)
lm.beta(Regression.s.k3.t2)
confint(lm.beta(Regression.s.k3.t2), level = 0.95)

res.lm <- residuals(Regression.s.k3.t2) 
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t2 ~ s.t1 + age.t2 + gender.t2.d + pol_orient.t2 + bed*t.t2, data = data))



par(mfrow = c(2, 2)) 
plot(Regression.s.k3.t2)       
par(mfrow = c(1, 1))  

car::vif(Regression.s.k3.t2) 


# Plotting interaction  

library(sjPlot)
library(sjmisc)
library(ggplot2)

Regression.s.k3.t2 <- lm(s.t2 ~ age.t2 + gender.t2.d + pol_orient.t2 + t.t2*bed, data = data)
plot_model(Regression.s.k3.t2, type = "int")


```

### Comparing models
Step 1 vs. 2
```{r}
anova(Regression.s.k.t2, Regression.s.k2.t2)
```

Step 2 vs. 3
```{r}
anova(Regression.s.k2.t2, Regression.s.k3.t2)
```

Step 1 vs. 3
```{r}
anova(Regression.s.k.t2, Regression.s.k3.t2)
```

## T3 {.tabset}
### Step 1
```{r}
Regression.s.k.t3 <- lm(s.t3 ~ age.t3 + gender.t3.d + pol_orient.t3, data = data)                
summary(Regression.s.k.t3)
lm.beta(Regression.s.k.t3)
confint(lm.beta(Regression.s.k.t3), level = 0.95)

res.lm <- residuals(Regression.s.k.t3) 
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t3 ~ s.t1 + s.t2 + age.t3 + gender.t3.d + pol_orient.t3, data = data))



par(mfrow = c(2, 2))  
plot(Regression.s.k.t3)   
par(mfrow = c(1, 1))  

car::vif(Regression.s.k.t3) 
```

### Step 2
```{r}
Regression.s.k2.t3 <- lm(s.t3 ~ age.t3 + gender.t3.d + pol_orient.t3 + bed + t.t3, data = data)   
summary(Regression.s.k2.t3)
lm.beta(Regression.s.k2.t3)
confint(lm.beta(Regression.s.k2.t3), level = 0.95)

res.lm <- residuals(Regression.s.k2.t3) 
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t3 ~ s.t1 + s.t2 + age.t3 + gender.t3.d + pol_orient.t3 + bed + t.t3, data = data))


par(mfrow = c(2, 2)) 
plot(Regression.s.k2.t3)         
par(mfrow = c(1, 1))  

car::vif(Regression.s.k2.t3)
```

### Step 3
```{r}
Regression.s.k3.t3 <- lm(s.t3 ~ age.t3 + gender.t3.d + pol_orient.t3 + bed*t.t3, data = data)   
summary(Regression.s.k3.t3)
lm.beta(Regression.s.k3.t3)
confint(lm.beta(Regression.s.k3.t3), level = 0.95)

res.lm <- residuals(Regression.s.k3.t3) 
describe (res.lm)
shapiro.test(res.lm)
dwt(lm(s.t3 ~ s.t1 + s.t2 + age.t3 + gender.t3.d + pol_orient.t3 + bed*t.t3, data = data))


par(mfrow = c(2, 2)) 
plot(Regression.s.k3.t3)    
par(mfrow = c(1, 1))  

car::vif(Regression.s.k3.t3)

# Plotting interaction 
Regression.s.k3.t3 <- lm(s.t3 ~ age.t3 + gender.t3.d + pol_orient.t3 + t.t3*bed, data = data)   
plot_model(Regression.s.k3.t3, type = "int")

```

### Comparing models
Step 1 vs. 2
```{r}
anova(Regression.s.k.t3, Regression.s.k2.t3)
```

Step 2 vs. 3
```{r}
anova(Regression.s.k2.t3, Regression.s.k3.t3)
```

Step 1 vs. 3
```{r}
anova(Regression.s.k.t3, Regression.s.k3.t3)
```

# Pre-registered analyses {.tabset}
## Pre-registered H1: ANCOVA
```{r}
result <- lm(s.t2~s.t1*bed,data = data)
summary.aov(result)

library(heplots) 
etasq(result, type = 2, anova = TRUE)

result <- lm(s.t3~s.t2*bed,data = data)
summary.aov(result)
etasq(result, type = 2, anova = TRUE)
```

## Pre-registered H2: t-Test T1 vs. T2 {.tabset}
### Testing assumptions
```{r}
leveneTest(data$s.t1, data$s.t2, center=mean) 

shapiro.test(data$s.t1)
shapiro.test(data$s.t2)
```

### Paired samples t-test
```{r}
t.test(data$s.t1, data$s.t2, paired=TRUE)
```

### Wilcoxon test
```{r}
wilcox.test(data$s.t1,data$s.t2,paired=TRUE)
```

### Cohen's d
```{r}
library(effsize)
library(car)
cohen.d(data$s.t1,data$s.t2, na.rm = TRUE, paired=TRUE, pooled = TRUE, mu=0)
```

## Pre-registered H3: see H3 above

## Pre-registered H4: see H5 above
## Pre-registered H5: see H6 above
## Pre-registered H6: see H7 above
## Pre-registered H7: t-Test T2 vs. T3 {.tabset}
### Testing assumptions
```{r}
leveneTest(data$s.t2, data$s.t3, center=mean) 

shapiro.test(data$s.t2)
shapiro.test(data$s.t3)
```

### Paired samples t-test
```{r}
t.test(data$s.t2, data$s.t3, paired=TRUE)
```

### Wilcoxon test
```{r}
wilcox.test(data$s.t2,data$s.t3,paired=TRUE)
```

### Cohen's d
```{r}
cohen.d(data$s.t2,data$s.t3, na.rm = TRUE, paired=TRUE, pooled = TRUE, mu=0)
```


# Comparing EG and CG at T1 {.tabset}
## Testing assumptions
```{r}
leveneTest(data$swb.t1, data$bed, mean) 
leveneTest(data$t.t1, data$bed, mean) 
leveneTest(data$gbk.t1.s, data$bed, mean) 
leveneTest(data$s.t1, data$bed, mean) 
leveneTest(data$sr.t1, data$bed, mean) 
leveneTest(data$age.t1, data$bed, mean) 
leveneTest(data$pol_orient.t1, data$bed, mean)
```

## t-tests
```{r}
t.test(data$swb.t1 ~ data$bed)
t.test(data$t.t1 ~ data$bed)
t.test(data$gbk.t1.s ~ data$bed)
t.test(data$s.t1 ~ data$bed)
t.test(data$sr.t1 ~ data$bed)
t.test(data$age.t1 ~ data$bed)
t.test(data$pol_orient.t1 ~ data$bed)
```

## d-score
```{r}
library(lsr)
cohensD(age.t1 ~ bed, data=data, method="pooled")
```

# Comparing completers vs. dropouts {.tabset}
```{r}
data$comp1 <- recode (data$ok.t2, 'NA=0; 1=1') #no participation at T2
data$comp2 <- recode (data$ok.t3, 'NA=0; 1=1') #no participation at T3

tabyl(data, comp1)
tabyl(data, comp2)
```

## T2 {.tabset}
### Testing assumptions
```{r}
leveneTest(data$swb.t1, data$comp1, mean) 
leveneTest(data$t.t1, data$comp1, mean) 
leveneTest(data$gbk.t1.s, data$comp1, mean) 
leveneTest(data$s.t1, data$comp1, mean) 
leveneTest(data$sr.t1, data$comp1, mean) 
leveneTest(data$age.t1, data$comp1, mean) 
leveneTest(data$pol_orient.t1, data$comp1, mean) 
```

### t-tests
```{r}
t.test(data$swb.t1 ~ data$comp1)
t.test(data$t.t1 ~ data$comp1)
t.test(data$gbk.t1.s ~ data$comp1)
t.test(data$s.t1 ~ data$comp1)
t.test(data$sr.t1 ~ data$comp1)
t.test(data$age.t1 ~ data$comp1)
t.test(data$pol_orient.t1 ~ data$comp1)
```

### Cohen's d
```{r}
cohensD(gbk.t1.s ~ comp1, data=data, method="pooled")
```

### Descriptives
```{r}
describeBy(data$gbk.t1.s, data$comp1, mat = TRUE)
```

## T3 {.tabset}
### Testing assumptions
```{r}
leveneTest(data$swb.t2, data$comp2, mean) 
leveneTest(data$t.t2, data$comp2, mean) 
leveneTest(data$gbk.t2.s, data$comp2, mean) 
leveneTest(data$s.t2, data$comp2, mean) 
leveneTest(data$sr.t2, data$comp2, mean) 
leveneTest(data$age.t2, data$comp2, mean) 
leveneTest(data$pol_orient.t2, data$comp2, mean)
```

### t-tests
```{r}
t.test(data$swb.t2 ~ data$comp2)
t.test(data$t.t2 ~ data$comp2)
t.test(data$gbk.t2.s ~ data$comp2)
t.test(data$s.t2 ~ data$comp2)
t.test(data$sr.t2 ~ data$comp2)
t.test(data$age.t2 ~ data$comp2)
t.test(data$pol_orient.t2 ~ data$comp2)
```